Treatment_Outcomes

### 2023-04-25 Anxiety_Vis.Rmd
prepped everything for markdowns.

```{r setup, include=FALSE}
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

### 2023-04-25 Data_Import.Rmd
prepped everything for markdowns.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

# Background Statistics
```{r}
### Bar Chart for Discharge Status ###
plot(Mothership2$DC_status_1)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)

@@

# Background Statistics
```{r}
### Bar Chart for Discharge Status ###

### 2023-04-25 Depression_Vis.Rmd
prepped everything for markdowns.

```{r}
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20

#Create a New Data Set with an Average Depression Variable
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
```

```{r}
#Plot the Depression Mean for Full Sample
ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
  geom_line(size=1,color="#0065A3")+
  geom_point(color="#0065A3")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
  theme(panel.background=NULL)

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")

>>>>

```{r}
Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

#Create a Time Variable
Mothership_Long$TxDay <- NA
Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20

#Create a New Data Set with an Average Anxiety Variable
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
```

```{r}
#Plot the Depression Mean for Full Sample
ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
  geom_line(size=1,color="#0065A3")+
  geom_point(color="#0065A3")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
  theme(panel.background=NULL) 
```

### 2023-04-25 Treatment_Outcomes.Rmd
prepped everything for markdowns.

---
title: "Treatment_Outcomes"
output: html_document
date: "2023-04-14"
---
```{r setup, include=FALSE}
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

@@

## CUDOS and CUXOS over time.

```{r}
# Depression symptoms df
CUDOS_Score <- select(Mothership,
                      Days_complete_1,Day1_CUDOS:Day40_CUDOS)

# Anxiety symptoms df
CUXOS_Score <- select(Mothership,
                      Days_complete_1,Day1_CUXOS:Day40_CUXOS)

@@

```{r}
#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
Mothership_Pre_Post <- Mothership
  mutate(Mothership_Pre_Post, 
            Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
         )

  Mothership
#2. Then create df with CUDOS and CUXOS scores
  # Depression

    CUDOS_Score <- select(Mothership,
                      Day1_CUDOS:Day40_CUDOS)

  # Anxiety
    CUXOS_Score <- select(Mothership,
                      Day1_CUXOS:Day40_CUXOS)

#3. Extract the valeues for each patient at their last day (length of stay)
    # mutate(Mothership_Pre_Post, 
    #         CUDOS_post = CUDOS_Score[
    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
    #                 Mothership_Pre_Post$Days_complete_W)],
    #         CUXOS_post = CUXOS_Score[
    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
    #                 Mothership_Pre_Post$Days_complete_W)]
    #      )
```

```{r}
CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]

#4. Extract the value for their first day 
CUDOS_pre<-Mothership$Day1_CUDOS
CUXOS_pre<-Mothership$Day1_CUXOS
AnxDep_PrePost <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
AnxDep_PrePost

#5. Create long dataframe

###### This is where I am. I'm trying to figure out how to create the long dataset
AnxDep_PrePost_Long <- gather(AnxDep_PrePost,ID1:CUXOS_post)
                              factor_key = "T")

Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                              factor_key = "T")
Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]

?gather()

>>>>

---
title: "Treatment_Outcomes"
output: html_document
date: "2023-04-14"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

@@

```{r, include=FALSE}
# # Depression symptoms df
# CUDOS_Score <- select(Mothership,
#                       Days_complete_1,Day1_CUDOS:Day40_CUDOS)
# 
# # Anxiety symptoms df
# CUXOS_Score <- select(Mothership,
#                       Days_complete_1,Day1_CUXOS:Day40_CUXOS)

@@

```{r, include=FALSE}
#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
# Mothership <- Mothership %>%
#   mutate(Mothership_Pre_Post, 
#             Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
#          )
# 
# Mothership$Days_complete_W
# 
# #2. Then create df with CUDOS and CUXOS scores
#   # Depression 
#   
#     CUDOS_Score <- select(Mothership,
#                       Day1_CUDOS:Day40_CUDOS)
# 
#   # Anxiety
#     CUXOS_Score <- select(Mothership,
#                       Day1_CUXOS:Day40_CUXOS)
#     
# #### Figure out how to:
#     #1. write a for /while loop to get a final value. 
#     #2. get values for NAs for days attended, 
#     #3. get values so this can go into the whole mothership dataset. 
#     
#     
#     
#     
# #3. Extract the valeues for each patient at their last day (length of stay)
#  Mothership <- mutate(Mothership,
#             # CUDOS_post = CUDOS_post)
#             CUXOS_post = CUXOS_post)
#     ##### Why is it not includeing NAs.
# 
# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
# CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
# 
# CUDOS_post
# Mothership %>%
#   mutate(Dep_post = CUDOS_post)
# 
# CUDOS_post
# #4. Extract the value for their first day 
# CUDOS_pre<-Mothership$Day1_CUDOS
# CUXOS_pre<-Mothership$Day1_CUXOS
# AnxDep_PrePost_test <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
# AnxDep_PrePost_test
# colnames(AnxDep_PrePost)[1] = "ID1"
# 
# AnxDep_PrePost_test
# ## This is where I am Figure out where to go from here *******************
# #5. Create long dataframe
# 
# AnxDep_PrePost_Lon <- gather(AnxDep_PrePost,ID1:CUXOS_post,factor_key = "T")
# 
# AnxDep_PrePost_Long <- pivot_longer(AnxDep_PrePost,ID1:CUXOS_post)
# 
# 
# AnxDep_PrePost_Long
# ?pivot_longer()
# 
# AnxDep_PrePost_Long <- AnxDep_PrePost_Long[order(AnxDep_PrePost_Long$ID1),]
# 
# Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
#                               factor_key = "T")
# Mothership_Long_RDQ
